---
title: "R Notebook"
output: html_notebook
---
Processes Kidney dataset
Selects and processes: selected_a(old embedding), selected_a_2(new embedding)
# Libraries
```{r warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(Seurat)
library(ggplot2)
library(bspec)
library(sctransform)
library(cowplot)
library(gridExtra)
library(dplyr)
library(patchwork)
library(sctransform)
library(glmGamPoi)
library(SeuratDisk)
library("parallel")
```
# Whole Dataset
kidney - whole dataset, 10605 samples
## Clean Data
```{r}
# ------- use previously created Seurat object -------
kidney <- readRDS(file = "../../data/kidney_demo_stewart.rds")

# ------- use processed ones, with mt regress -------
# kidney <- readRDS(file = "../../data/kidney_data/kidney_mt_regress.rds")
# kidney_snn <- readRDS(file = "../../data/kidney_data/kidney_mt_snn_regress.rds")

# ------- use processed ones, without mt regress -------
# kidney <- readRDS(file = "../../data/kidney_data/kidney.rds")
# kidney_snn <- readRDS(file = "../../data/kidney_data/kidney_snn.rds")
```

```{r}
kidney[["percent.mt"]] <- PercentageFeatureSet(kidney, pattern = "^MT-")

kidney <- subset(kidney, subset = nFeature_RNA > 203 & nFeature_RNA < 7000 & nCount_RNA > 254 & nCount_RNA < 40000 & percent.mt < 20) 
```

## Reduce dimensions
```{r}
kidney <- SCTransform(kidney, vars.to.regress = "percent.mt", method = "glmGamPoi", verbose = FALSE)
kidney <- RunPCA(kidney, features = VariableFeatures(object = kidney))
```

```{r, eval=FALSE}
kidney[["kidney_general"]] <- "kidney_cells"
VlnPlot(kidney, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), group.by = "kidney_general", ncol = 3)

plot1 <- FeatureScatter(kidney, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "kidney_general")
plot1

ncol(kidney)
```

## Find SNN
```{r}
n = ncol(kidney)
dim(kidney)

type = c("_", "_trimmed_", "_negedges_", "_trimmed_negedges_")
id_type = 2
dim = 30
k = 5
coff = 0.067 #1/15
ord = 15

kidney <- FindNeighbors(kidney, reduction = "pca", dims = 1:dim, k.param=k, compute.SNN=TRUE, prune.SNN=coff)
```

```{r, eval=FALSE}
kidney_snn_temp <- kidney@graphs[["SCT_snn"]]

dim(kidney_snn_temp)
kidney_snn <- kidney_snn_temp - diag(nrow=n, ncol=n)
```

```{r, eval=FALSE}
# ------- limitation of nodes degrees -------
for (i in 1:n){
  to_delete <- order(kidney_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  kidney_snn[,i][to_delete] <- integer(n-ord)
  kidney_snn[i,][to_delete] <- integer(n-ord)
}
```

## Plot and save graphs 
```{r setup}
library(reticulate)
virtualenv_create("scrna_proj")
# py_install(c("networkx","matplotlib"), envname = "scrna_proj")
use_virtualenv("scrna_proj")
```

```{python, eval=FALSE}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

id_type, type = int(r.id_type)-1, r.type
n = int(r.n)
k = int(r.k)
ord = int(r.ord)
dim = int(r.dim)

file_name = ''.join(["../../graphs/kidney/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), ".gexf"])

G = nx.from_numpy_matrix(r.kidney_snn)
nx.write_gexf(G, file_name)

G = nx.read_gexf(file_name)
pos = nx.spring_layout(G)
plt.cla()
nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

file_name = ''.join(["../../graphs/kidney/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), ".png"])
plt.savefig(file_name, bbox_inches='tight')
```

## Clustering
```{r}
DimPlot(kidney, reduction = "pca", group.by="celltype") + NoLegend()
```

```{r}
kidney <- RunUMAP(kidney, reduction = "pca", dims = 1:10)
DimPlot(kidney, reduction = "umap", group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) + NoLegend()
```

```{r, eval=FALSE}
# ------- k-means -------
km.out <- kmeans(kidney@assays$SCT@data %>% as.matrix %>% t %>% as.data.frame, centers=12, nstart=5)
kidney <- AddMetaData(kidney, metadata=km.out$cluster, col.name="kmeans")
DimPlot(kidney, reduction = "umap", group.by="kmeans") # + NoLegend()
```

```{r, eval=FALSE}
# ------- Seurat clustering -------
kidney <- FindClusters(kidney, verbose = FALSE, resolution = 0.2, algorithm = 1)
DimPlot(kidney, reduction = "umap", group.by="seurat_clusters") # + NoLegend()
```

```{r}
# ------- Seurat clustering -------
kidney <- FindClusters(kidney, verbose = FALSE, resolution = 0.8, algorithm = 1)
DimPlot(kidney, reduction = "umap", group.by="seurat_clusters") # + NoLegend()
```

# Selected subset
selected_a - includes cells [Myofibroblast, vasa recta endothelium, Peritubular capillary endothelium]; trimmed to 1000 cells; original embedding derived from the whole dataset
selected_a_2 - the same as selected_a, but with the new embedding
## Select and Transform Data
```{r}
unique(kidney$celltype)
```

```{r}
to_select <- c("Myofibroblast", "Descending vasa recta endothelium", "Peritubular capillary endothelium 2", "Peritubular capillary endothelium 1", "Ascending vasa recta endothelium")
selected_meta <- is.element(kidney$celltype, to_select)
kidney <- AddMetaData(kidney, metadata=selected_meta, col.name="selected")
selected_a <- subset(x = kidney, subset = selected == TRUE)
ncol(selected_a)
selected_a <- selected_a[,colnames(selected_a)[1:1000]]
ncol(selected_a)
```

```{r}
selected_a_2 <- SCTransform(selected_a, vars.to.regress = "percent.mt", method = "glmGamPoi", verbose = FALSE)
selected_a_2 <- RunPCA(selected_a_2, features = VariableFeatures(object = selected_a_2))
```

```{r}
selected_a_2 <- RunUMAP(selected_a_2, dims = 1:30, verbose = FALSE)
selected_a_2 <- FindNeighbors(selected_a_2, dims = 1:30, verbose = FALSE)
selected_a_2 <- FindClusters(selected_a_2, resolution = 0.1, verbose = FALSE)
```

```{r}
DimPlot(selected_a, label = TRUE, label.size = 3, group.by="seurat_clusters") #+ NoLegend()
DimPlot(selected_a, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
```

```{r}
DimPlot(selected_a_2, label = TRUE, label.size = 3, group.by="seurat_clusters") #+ NoLegend()
DimPlot(selected_a_2, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
```

## Generate SNN graph
```{r}
n = ncol(selected_a_2)
dim(selected_a_2)

type = c("_", "_trimmed_", "_negedges_", "_trimmed_negedges_")
id_type = 2
dim = 30
k = 10
coff = 0.067 #1/15
ord = 15

selected_a_2 <- FindNeighbors(selected_a_2, reduction = "pca", dims = 1:dim, k.param=k, compute.SNN=TRUE, prune.SNN=coff)

selected_a_2_snn_temp <- selected_a_2@graphs[["SCT_snn"]]

dim(selected_a_2_snn_temp)
selected_a_2_snn <- selected_a_2_snn_temp - diag(nrow=n, ncol=n)
```

```{r}
isSymmetric(selected_a_2_snn)
```

```{r}
# ------- limitation of nodes degrees SYMMETRICS-------
for (i in 1:n){
  to_delete <- order(selected_a_2_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  selected_a_2_snn[,i][to_delete] <- integer(n-ord)
  selected_a_2_snn[i,][to_delete] <- integer(n-ord)
}
```

```{r, eval=FALSE}
# ------- limitation of nodes degrees UNSYMMETRIC -------
for (i in 1:n){
  to_delete <- order(selected_a_2_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  selected_a_2_snn[,i][to_delete] <- integer(n-ord)
}
```

```{r, eval=FALSE}
# ------- Enhance shared edges (may want to repeat multiple times) -------
library(Matrix)

# Method 1
selected_a_2_snn_old <- selected_a_2_snn
for (i in 1:n){
    selected_a_2_snn[i,] <- selected_a_2_snn_old[i,]+selected_a_2_snn_old[,i]
}

# Method 2
mutual = matrix(0,n,n)

for (i in 1:n){
    mutual[i,] <- selected_a_2_snn[i,] & selected_a_2_snn[,i] 
}
nnzero(mutual)

selected_a_2_snn_old <- selected_a_2_snn
for (i in 1:n){
    selected_a_2_snn[i,] <- selected_a_2_snn_old[i,]+mutual[,i]
}
```

## Plot and save graphs 
```{python}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

id_type, type = int(r.id_type)-1, r.type
n = int(r.n)
k = int(r.k)
ord = int(r.ord)
dim = int(r.dim)

file_name = ''.join(["../../graphs/kidney/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), ".gexf"])

G = nx.from_numpy_matrix(r.selected_a_2_snn)
nx.write_gexf(G, file_name)

G = nx.read_gexf(file_name)
pos = nx.spring_layout(G)
plt.cla()
nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

file_name = ''.join(["../../graphs/kidney/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), ".png"])
plt.savefig(file_name, bbox_inches='tight')
```

```{r}
knitr::include_graphics(py$file_name)
```